% 
% 
% vim: tabstop=2 shiftwidth=2 expandtab noautoindent nosmartindent

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://euclideansphere.github.io}{\Large Austin Hartline}} & Email: \href{mailto:austin.dev@protonmail.com}{austin.dev@protonmail.com}\\
  \href{https://euclideansphere.github.io/}{https://euclideansphere.github.io} & Mobile: +1 414-334-4061 \\
\end{tabular*}

\section{Objective}

Proven engineer with 7+ years FTE experience seeking senior backend focused SWE role with opportunity to mentor, be mentored, and think critically about how to best empower decision makers with the data they need to be successful.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Milwaukee School of Engineering}{Milwaukee, WI}
      {Bachelor of Science in Software Engineering; GPA: 3.8}{Sep. 2013 -- May. 2017}

    \item\small{
      Eagle Scout; BSA
    }

  \resumeSubHeadingListEnd

\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: SQL, Ruby, Typescript, C\#, Terraform, Python}
   }
   \item{
     \textbf{Technologies}{: PostgreSQL, ReactJS, Ruby on Rails, NodeJS, AWS}
   }
 \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Contracting, Self Employment}{(Remote) Milwaukee, WI}
      {Software Contractor}{Jul 2023 - Present}
      \resumeItemListStart
        \resumeItem{Rapid Delivery}
          {Prototype, build, and iterate on key features with tight deadlines to win customers and obtain Series A funding for a CMMS startup (NodaFi).}
        \resumeItem{Javascript, Node}
          {Build full stack features for a React-Native mobile app and a React web app backed by a GraphQL NestJS (NodeJS) web API.}
        \resumeItem{Performance}
          {Instrument DataDog telemetry and use MariaDB (MySQL) query planner to troubleshoot and improve critical page performance.}
        % \resumeItem{Elixir}
        %   {Bootstrap a Phoenix / Elixir / PostgreSQL personal budget tracking application using Plaid.}
      \resumeItemListEnd

    \resumeSubheading
      {Betterment, Inc}{(Remote) New York, NY}
      {Full Stack Engineer III}{Jan 2022 - Jun 2023 (layoff)}
      \resumeItemListStart
        \resumeItem{Ruby on Rails}
          {Design and build Ruby on Rails REST APIs, collaborating with mobile development while planning for concurrent ReactJS and StimulusJS web consumers.}
        \resumeItem{Data Engineering}
          {Lead data engineering financial audit project orchestrated with Airflow, DBT (ETL and job definition solution) against an AWS Redshift Data Warehouse to provide required proofs to regulators.}
        \resumeItem{Mentorship, Leadership}
          {Mentor junior developer on temporal SQL query optimization, data modeling, estimation, and negotiating project scope to foster IC growth.}
        % \resumeItem{Fintech}
        %   {Update React / Typescript flows to handle changing IRS rules around tax advantaged accounts}
        \resumeItem{Testing}
          {Ensure software behavioral correctness using Jest, RSpec, DBT test, and in-house open-source software testing solutions to prevent escaped defects.}
        % \resumeItem{Design}
        %   {Co-lead writing the design proposal of recurring transfers implementation, providing data modeling and Ruby on Rails expertise.}
        \resumeItem{Design}
          {Write technical design proposal to build organizational concensus around novel account access mechanisms to allow implementation of recurring transfers.}
        % \resumeItem{Plaid}
        %   {Use DataDog to monitor, report, and plan Plaid integration fault tolerance and robustness improvements.}
        \resumeItem{Javascript}
          {Became a designated organization wide Javascript Platform Reviewer to provide technical support to peers and influence company web frontend standards.}
        \resumeItem{On Call Responsibility}
          {Participate in team and organization on-call processes, handling customer tickets and coordinating support for live production outages.}
      \resumeItemListEnd

    \resumeSubheading
      {GenoPalate, Inc}{(Remote) Milwaukee, WI}
      {Software Engineer (Mid-Senior Level)}{Sep 2020 - Jan 2022}
      \resumeItemListStart
        \resumeItem{Javascript, Node}
          {Collaborate with a small team to estimate, scope, and build features for a React-Native mobile application and a React web frontend backed by an ExpressJS / Knex (NodeJS) web service.}
        % \resumeItem{Typescript Migration}
        %   {Scope, document a plan, and lead migration effort to add type checking (Typescript) to all JS code and reduce escaped defects.}
        \resumeItem{Integration}
          {Communicate with external vendors to design and implement DNA data integrations, automating all manual process from shipment to DNA sample processing and DNA sequence ingestion.}
        \resumeItem{Influence Team}
          {Advocate for, plan, and lead effort to standardize testing (Jest), implement type checking (Typescript), code review, deployment, and error monitoring (Sentry) to reduce escaped defect rate by 90\%.}
        \resumeItem{Agile}
          {Participate in Agile / SCRUM process, including collaborative design sessions with stakeholders, iterative delivery, team estimations, and building consensus.}
        % \resumeItem{Product Design}
        %   {Participate in product design sessions and influence product direction.}
        \resumeItem{Node and PostgreSQL}
          {Own and fix complex technical issues with RDBMS Node runtime and data corruption to eliminate production outages.}
        \resumeItem{PostgreSQL}
          {Draft written plan and execute project to upgrade AWS RDS PostgreSQL instance without any unplanned downtime.}
        % \resumeItem{Authentication OWASP Compliance}
        %   {Propose, draft design, and lead rebuild of Redis JWT based authentication system for improved security and multi-session support.}
        \resumeItem{Shopify Integration}
          {Build robust fault tolerant support for Shopify order integration in Node / Typscript on AWS (ECS, Lambda, SQS, S3) to ingest every customer purchase.}
        % \resumeItem{UX Support}
        %   {Support UX developer in building shopify ordering workflow}
        \resumeItem{Cloud Infrastructure / DevOps}
          {Pitch, plan, and lead project to standardize all AWS infrastructure deployment and CI/CD through Github Actions, Terraform (IaC), and Docker to eliminate clickops deployment error.}
        % \resumeItem{Genomic Informatics}
        %   {Improve genomic data mining algorithms (AWS Step Functions, Python, Parquet, AWS Athena, Javascript) through data model normalization (PostgreSQL) and rigorous backtesting.}
        % \resumeItem{Research}
        %   {Prototype and demo graph based (Neo4J) recipe generation solution using NLP.}
      \resumeItemListEnd

    \vspace{4pt}
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{Travel Break} & \textit{\small Jun 2020 - Aug 2020} \\
      \end{tabular*}\vspace{-5pt}

    \resumeSubheading
      {Wantable}{Milwaukee, WI}
      {Senior Software Engineer}{Feb 2019 - May 2020}
      \resumeItemListStart
        \resumeItem{React, Typescript}
          {Assist lead UX designer in building a Typescript, React, and SCSS design system to replace CSS style guide to create a coherent automatable UX.}
        \resumeItem{Data Science}
          {Integrate rich Python / R data science models into dynamic React / Rails UIs to enable internal users to make quantitatively smarter decisions.}
        \resumeItem{Project Ownership}
          {Prototype, and iteratively deliver customer facing e-commerce solutions using Rails, Redis, PostgreSQL and AngularJS to sell more product.}
        % \resumeItem{Ruby on Rails}
        %   {Standardize product data quality on all new products by building PIM solutions in AngularJS and React (Typescript).}
        % \resumeItem{Testing}
        %   {Write automated tests using RSpec.}
        \resumeItem{Warehouse Management}
          {Build and improve warehouse logistics and inventory management solutions in .NET and Ruby on Rails to reduce labor inefficiency.}
        \resumeItem{Data Integration}
          {Build and optimize Rails (ARel) and PostgreSQL export jobs to marketing channels to reduce cloud compute costs by \$2,000/month and improve customer acquisition, churn, and lifetime value metrics.}
        % \resumeItem{Heroku}
        %   {Deploy and monitor a monolithic Rails application on Heroku.}
        \resumeItem{Performance Monitoring}
          {Use New Relic, Sentry, and Lighthouse to improve user facing page and image load performance, which improved SEO and sales metrics.}
        % \resumeItem{On Call Responsibility}
        %   {Participate in on-call rotation including handling support tickets and solving live production issues.}

        % TODO:
        % \resumeItem{Iterative Delivery}
        %   {Iteratively uplift and improve rich interactive dashboards for stylists to pick clothes for customers based on integrated data science models, a recommender system, warehouse inventory metrics, and customer preferences in React, Typescript, Ruby on Rails, and Python.}

      \resumeItemListEnd

    \resumeSubheading
      {Direct Supply, Inc}{Milwaukee, WI}
      {Sotware Engineer}{May 2017 - Feb 2019}
      \resumeItemListStart
        \resumeItem{.NET Development}
          {Develop features and integrations for a catalog based food and equipment ecommerce solution in the eldercare industry using C\#, Razor, Typescript, ReactJS, CoffeeScript, AngularJS.}
        \resumeItem{Domain Driven Development}
          {Demonstrate strong understanding of CAP theorum and distributed computing by designing and building fault tolerant integrations between disjointed lines of business and domains.}
        \resumeItem{Microservices}
          {Collaborate with team to design and build 12 factor microservices in C\#, SQL Server, and documented with OpenAPI to automate quote generation and work order tasks.}
        \resumeItem{Microservice Cloud Infrastructure}
          {Lead setup of automated infrastructure deployment to AWS ECS Fargate / AWS RDS (SQL Server) using Terraform, Hashicorp Vault, Bash, Docker, and Gitlab Pipelines.}
        \resumeItem{Terraform}
          {Pioneer IaC implementation (Terraform) and educate several teams of engineers how to deploy to multiply org efficiency.}
        \resumeItem{Open Source Contribution}
          {Identify and fix defects in Terraform AWS Provider (golang) to improve deploy idempotency.}
        % \resumeItem{DbUp}
        %   {Write and deploy SQL Server schema and stored procedures using DbUp to .}
        \resumeItem{Event Driven Architecture}
          {Use AWS Lambda, PostgreSQL, RabbitMQ to connect distributed systems and automate services procurement.}
        % \resumeItem{Xamarin}
        %   {Build features for a Xamarin mobile application in .NET.}
        % \resumeItem{Testing}
        %   {Implement unit and integration tests using MSTest, Cucumber / Gherkin, Moq, Jasmine, Jest, Mocha.}
        \resumeItem{Mentorship}
          {Mentor intern and junior developers to increase team velocity and foster team strength.}
        % \resumeItem{Shell Scripting}
        %   {Use PowerShell to refactor and decouple segments of a large .NET monolithic code base for improved build times and developer experience.}
        \resumeItem{LEAN UX User Testing}
          {Use LEAN UX methodology to perform direct user research with prototypes and A/B testing to reduce feature risk and improve delivery confidence.}
        % \resumeItem{Monitoring, System Ownership}
        %   {Monitor live production performance and influence feature prioritization using New Relic telemetry metrics.}

      \resumeItemListEnd

    \resumeSubheading
      {Direct Supply, Inc}{Milwaukee, WI}
      {Sotware Engineer (Intern)}{Jan 2014 - May 2017}
      \resumeItemListStart
        % \resumeItem{IIS}
        %   {Learn, repair, and replace legacy asp procurement system served by IIS.}
        % \resumeItem{ASP}
        %   {Work with QA to fix print media rendering issues and IE bugs in asp and ASP.NET pages.}
        % \resumeItem{Legacy System Management}
        %   {Fix bugs in legacy procurement financial batch jobs in VB6, VC++08, .NET, T-SQL.}
        % \resumeItem{Leadership}
        %   {Lead summer intern project for 17 interns, which invovled: crafting a project idea, organizing meeting space, soliciting executive approval, delivering weekly status updates, and presenting a final demo.}
        % \resumeItem{Mentorship}
        %   {Mentor other interns on technical concepts and through their tasks.}
        \resumeItem{RabbitMQ}
          {Integrate RabbitMQ event broker to satisfy user needs across lines of business.}
        \resumeItem{.NET Modernization}
          {Participate in an agile team (full time as of 2016) to modernize 100s of legacy jobs and distributed web systems to a modern .NET on AWS cloud based architecture.}
        % \resumeItem{Agile / SCRUM}
        %   {Participate in Agile Methodology (SCRUM) though daily standups, grooming, estimation, sprint review, quarterly company wide demonstrations.}
        % \resumeItem{Testing}
        %   {Influence the team and technical leadership to adopt more robust testing practices.}
        % \resumeItem{Deployment}
        %   {Organize and perform software releases off hours (including writing deploy and testing procedure, writing post mortems when things go wrong).}
        % \resumeItem{Legacy System Management}
        %   {Migrate hundreds of legacy batch jobs from legacy clickops job orchestrator to automated Octopus Deploy, with CI/CD, auditing each for security vulnerability, proper access control, and VCS tracking.}
        % \resumeItem{Integration}
        %   {Build authorized iframe based integrations to external vendors and other internal lines of business.}
        % \resumeItem{Frontend Development}
        %   {Tackle frontend ASP.NET MVC development needs using Razor views, AngularJS, Coffeescript, JQuery, Javascript, Bower, Backbonejs.}
        \resumeItem{SQL}
          {Investigate and fix high I/O SQL deadlocking issues, with over 1000 transactions per second.}
        % \resumeItem{Cross Team Collaboration}
        %   {Coordinate frontend feature development with other teams release schedules and coding standards for systems not owned by my team.}

      \resumeItemListEnd

  \resumeSubHeadingListEnd


% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{SuperMileage Vehicle}
%       {Build telemetry system for prototype high efficiency vehicles using Python and Android SDK.}
%   \resumeSubHeadingListEnd


\end{document}

