% LaTeX resume using res.cls
\documentclass[line,margin]{res}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\topmargin=-0.5in
\oddsidemargin=-0.5in
\evensidemargin=-0.5in
\textwidth=5.5in
\textheight=800pt
\itemsep=0in
\parsep=0in
\footskip=0in
%\resumewidth=6.5in
%\setlength{\textwidth}{6.5in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
\name{Austin Hartline}
% Draw a horizontal line the whole width of resume:
%\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

% phone number is described using math monospace unicode letters to mitigate some spam.
\address{austin.dev@protonmail.com | (414) 334-4061}

\begin{resume}

\section{OBJECTIVE}
Seeking senior backend focused software role with exposure to high data throughput systems and data analytics.

\section{EDUCATION}
{\sl Bachelor of Science,} Software Engineering \\
Milwaukee School of Engineering (WI) \hfill May 2017 \\
GPA: 3.75, High Honors \\

\section{EXPERIENCE}

\textbf{NodaFi, Inc} \hfill Jul 2023 - present \\
{\sl Indepdendent Contractor (Developer)}

Implement key features and optimization to win customers and secure seed funding for an early stage CMMS startup.

\begin{itemize}
\item Instrument telemetry to trace, prioritize, and resolve performance degradation
\item NodeJS, React, React-Native, Datadog
\end{itemize}

\textbf{Betterment, Inc} \hfill Jan 2022 - Jun 2023 \\
{\sl Full Stack Engineer III}

Plan, design, lead, and develop solutions for an investment bank (fintech).

\begin{itemize}
\item Lead audit automation project for financial regulators (SQL, Python, Airflow)
\item Mentor peers for data modelling \& SQL query performance optimization tasks
\item Trace, benchmark, and improve Plaid integration
\item Ruby on Rails, PostgreSQL, React, Typescript, Airflow, AWS, Datadog, Redshift, Python
\end{itemize}

\textbf{GenoPalate, Inc} \hfill Sep 2020 - Jan 2022 \\
{\sl Product Engineer}

Prototype and build out a DNA based personalized nutrition app.

\begin{itemize}
\item Strategize and advocate for agile process improvements (SCRUM)
\item Retrofit Terraform to existing manually deployed AWS infrastructure
\item NodeJS / Express, PostgreSQL, React, AWS Lambda, SQS, Shopify
\end{itemize}

\textbf{Wantable, Inc.} \hfill Feb 2019 - May 2020 \\
{\sl Senior Full Stack Rails Developer}

Architect, implement, and maintain software for an ecommerce clothing business, especially for warehouse management.

\begin{itemize}
\item Architect and build solutions for warehouse operations and clothing curation
\item Integrate data science modelling to empower internal decision makers
\item Ruby on Rails, PostgreSQL, Heroku, AngularJS, Typescript, React
\end{itemize}

\textbf{Direct Supply, Inc.} \hfill Jan 2014 -- Feb 2019 \\
{\sl Software Engineer} \hfill {\sl May 2017 -- Feb 2019} \\
{\sl Software Engineer, Intern} \hfill {\sl Jan 2014 -- May 2017}

Design, develop, and maintain software products \& ecommerce solutions for Eldercare Industry.

\begin{itemize}
\item Migrate monolithic legacy systems to a microservice architecture. 
\item AWS, Microservices, Terraform, SQL Server, React, ASP.NET, C\#, Typescript, VB6 \& COM
\end{itemize}

%\section{SKILLS}
%SQL, Ruby on Rails, C\# / .NET, React, Bash, Javascript, Typescript

%\section{PROJECTS}

%{\sl SAE SuperMileage} \hfill September 2013 -- June 2016
%\begin{itemize}
%\item Design and build electrical \& telemetry system for prototype vehicles
%\end{itemize}

{\sl Eagle Scout, BSA}

GitHub Username: euclideansphere

\end{resume}

\end{document}

